---
title: "Heat Study: Updates 4.20.26"
format:
  revealjs:
    theme: simple
    slide-number: true
---


## Working with NREL 15 minute data
:::: {.columns}

::: {.column width="50%"}
#### Directory Structure
```{r}
#| echo: false
#| warning: false



fs::dir_tree(
    here::here(
        'partition_diagram'
        )
)
```

::: {.incremental}
- The data live in a **hive partitioned** hosted on an **s3 bucket**. 1 file = 1 building's 15 minute increment output.
- They're deployed this way because of the dataset's size (It's over 17 billion rows 🤯)
:::

:::


:::  {.column width="50%"}
::: {.fragment}
#### File Itself 

```{r}
library(tidyverse)

read_csv(
    here::here('pa_sample_from_nrel_bucket.csv')) |>
  select(
    bldg_id,
    timestamp,
    cooling_load =
      out.indoor_temperature.conditioned_space..c
  ) |>
  slice_head(n = 8) |>
  tinytable::tt() |> 
tinytable::style_tt(fontsize = 0.55)


```

- The building files themselves are one row of data per 15 minute energyPlus output. 

:::
:::

::::

##  Working with NREL 15 minute data

::: {.incremental}
1. Specialized tools like [duckdb](https://duckdb.org/), an embedded analytics database, can access these data structures efficiently.
1. Because data are partitioned, we can skip reading the data that we don't need. 
1. We can write SQL directly against the bucket, so only the aggregated results come into R
:::
