---
title: "Heat Study: Updates 4.20.26"
format:
  revealjs:
    theme: simple
    slide-number: true
---


## Where We Are {.smaller}

::: {.columns}

::: {.column width="5%"}
:::

::: {.column width="90%"}

::: {.incremental}

1. **Switched data sources**: Moved from RECs to **NREL ReStock** for housing characteristics and indoor temperature — better geographic coverage, higher N, and far richer indoor environment data.

2. **Linkages didn't hold up**: When we validated RECs–PUMS linkages using ReStock as ground truth, performance was poor.

3. **New strategy**: Instead of trying to link multiple housing characteristics at once, we build **predictive models of indoor temperature** and apply them out-of-sample to PUMS / MDAC. To practice, we've built and assessed models predicting indoor cooling load using the annual ReStock data.

4. **Next step**: We can sharpen predictions further with more granular (daily?) target variables and a newly released **indoor temperature** variable for model training.

:::
:::

::: {.column width="5%"}
:::

:::

## Working with NREL 15 minute data
:::: {.columns}

::: {.column width="50%"}
#### Directory Structure
```{r}
#| echo: false
#| warning: false



fs::dir_tree(
    here::here(
        'partition_diagram'
        )
)
```

::: {.incremental}
- The data live in a **hive partitioned** hosted on an **s3 bucket**. 1 file = 1 building's 15 minute increment output.
- They're deployed this way because of the dataset's size (It's over 17 billion rows 🤯)
:::

:::


:::  {.column width="50%"}
::: {.fragment}
#### File Itself 

```{r}
library(tidyverse)

read_csv(
    here::here('pa_sample_from_nrel_bucket.csv')) |>
  select(
    bldg_id,
    timestamp,
    cooling_load =
      out.indoor_temperature.conditioned_space..c
  ) |>
  slice_head(n = 8) |>
  tinytable::tt() |> 
tinytable::style_tt(fontsize = 0.55)


```

- The building files themselves are one row of data per 15 minute energyPlus output. 

:::
:::

::::

##  Working with NREL 15 minute data

::: {.incremental}
1. Specialized tools like [duckdb](https://duckdb.org/), an embedded analytics database, can access these data structures efficiently.
1. Because data are partitioned, we can skip reading the data that we don't need. 
1. We can write SQL directly against the bucket, so only the aggregated results come into R
:::
